---
title: "myvignette"
author: "Cemre Yilmaz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{myvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(earthquakes)
```
This is my capstone project in the specialization program of "Mastering Software 
Development in R Professional Certificate" by Roger D. Peng and Brooke Anderson 
on Coursera. This package is created to work with the NOAA Significant Earthquakes
dataset. It includes the following functions:
* ** `eq_clean_data` ** which cleans the data.
    + It creates the fields Date (in date format), Longitude (in numeric format) 
    and Latitude (in numeric format).
* ** `eq_location_clean` ** which arranges the location info.
    + It creates the fields Country in which country the earthquake happened.
    + It removes the country name from the field Location.Name.
* ** `geom_timeline` ** which plots every earthquake from the min to max date.
    + The color indicates the number of deaths.
* ** `geom_timeline_label` ** which plots every earthquake from the min to max date.
    + The color indicates the number of deaths.
    + A lebel is shown for the earthquakes of which magnitude is above the threshold.
* ** `eq_map` ** which creates an interactive map to show the geographical locations
of the earthquakes in data.
    + The size of circle represents the magnitude of the corresponding earthquake.
    + When you click on a circle, you can see the the chosen annotation as pop-up.
* ** `eq_create_label` ** which creates the pop-up message for eq_map() function.
